A neural coarse graining theory of consciousness

### 2018-07-05 Paper_neural_coarse_graining_of_consciousness.tex
Rearranged

			\begin{figure}
				\includegraphicsTodo[width=\textwidth]{WritingMaterials/PDFXCview_2018-06-07_17-45-59.png} 
				\cite{BERTSCHINGER.2006} I need something like this 
				\caption{xxxx}
				\label{fig:AgentAndEnv}			
			\end{figure}

			\begin{ants}				
				@ Formally, then, a system is informationally closed if (almost) no information flows into it from the environment.

				@ \rewrite{
					The notion of informational closure refers to a situation where the information flow between the environment and the system tends to zero.} \cite{BERTSCHINGER.2006}

				@ Mathematically, informational closure can be define and measured by as the degree of information flowing from the environment to a system.
				\begin{equation}\label{eq:InformationFlow}
				\left.\begin{array}
				{rl}{J_{n}(E \rightarrow S )} & { = MI(S_{n+1};E_{n}|S_{n})} \\
				{ } & { = H(S_{n+1}|S_{n})-H(S_{n+1}|S_{n},E_{n})} \\
				{ } & { = H(E_{n}|S_{n})-H(E_{n}|S_{n},S_{n+1})} \\
				{ } & { = H(E_{n}|S_{n})-H(E_{n}|S_{n},S_{n+1})}
				\end{array}\right.
				\end{equation}

				@ \ref{eq:InformationFlow} can be rewritten as 
				\begin{equation}
				MI(S_{n+1};E_{n}|S_{n}) = 
				MI(S_{n+1};E_{n}) - (MI(S_{n+1};S_{n})-MI(S_{n+1};S_{n}|E_{n}))
				\end{equation}

@@

	\section{A neural coarse graining theory of consciousness}
		\toWrite{Need to describe my intuition more concretely }

@@

			%% our claim 
				@

@@

			\begin{figure}[H]
				\includegraphics[width=\textwidth]{WritingMaterials/HierachyDiscussion (1).jpg}
%				{Coarse-grain and sensory anatomical hierarchies}
			\end{figure}

@@

	\section{Biological evidence of informational closure in neural system}

		\begin{ants}		
			% ============================================================================ %
			%                             sederberg2018learning                            %
			% ============================================================================ %

	\section{Relation to empirical findings in neuroscience and studies of consciousness}

	\section{About Phenomenology (conscious processing)}
		\subsection{Perceptual overflow}
		\subsection{Volition and freewill}
			\begin{ants}
				@ Volition is a result of coarse-graining

	\section{Comparison with other theories}

@@

	\section{Theory predictions (Counter-intuitive prediction)}

@@

>>>>

			\noindent Information flow $J_{t}$ from environment $E$ to a system $Y$ at time $t$ can be defined as			
				\begin{equation}\label{eq:InformationFlow}
				\left.\begin{array}
				{rl}{J_{t}(E \rightarrow Y )} & {:= I(Y_{t+1};E_{t}|Y_{t})} \\
				%{ } & { \ = H(Y_{t+1}|Y_{t})-H(Y_{t+1}|Y_{t},E_{t})} \\
				%{ } & { \ = H(E_{t}|Y_{t})-H(Y_{t}|Y_{t},Y_{t+1})} \\
				%{ } & { \ = H(E_{t}|Y_{t})-H(E_{t}|Y_{t},Y_{t+1})}\\
				{ } & { \ = I(Y_{t+1};E_{t}) - (I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t}))}
				\end{array}\right.
				\end{equation}

				\begin{figure}
					\includegraphics[width=\textwidth]{WritingMaterials/SystemAndEnv.pdf} 
					\caption{Figure adapted from \cite{BERTSCHINGER.2006}}
					\label{fig:SystemAndEnv}	
				\end{figure}

			\noindent
			Based on the definition from \cite{BERTSCHINGER.2006}, a system is informational closured when information flow between the environment and the system is close to zero.

			\noindent However, achieving information closure (minimising $J_t$) could be trivial, which means the environment and the system are entirely independent of each other.
				\begin{equation}
				\begin{aligned}
				{I(Y_{t+1};E_{t})=0}&&{\Rightarrow}&&{J_{t}(E \rightarrow Y )=0}
				\end{aligned}
				\end{equation}

			\noindent In the non-trivial case, the system trying to encode environmental dynamic can also achieve informational closure. This means
				\begin{equation}
				I(Y_{t+1};E_{t})\neq0, 
				\end{equation}

			\noindent And, non-trivial informational closure can be defined as 		
				\begin{equation}
				\left.\begin{array}
				{rl}{NTIC} & {:=I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t})}\\
				{ } & {\ =I(Y_{t+1};E_{t})-I(Y_{t+1};E_{t}|Y_{t})}
				\end{array} \right.
				\end{equation}

			\noindent Therefore, Maximising NTIC is equivalent to
				\begin{equation}
				\begin{aligned}
				& \text{maximise} & { } & I(Y_{t+1};Y_{t}) & { } & \text{and} \\
				& \text{minimise} & { } & I(Y_{t+1};Y_{t}|E_{t}) & { }
				\end{aligned}
				\end{equation}

@@

	\section{A neural coarse graining theory of consciousness}
		\ideaBox{Need to describe my intuition more concretely}

		\begin{ants}
			\toWrite{Do I need to start with my philosophical intuition?}

			@ Through coarse-graining, we can define a new set of variables.

			@ If the new set of variables are informational closured, then this creates a new "reality" for all the variables inside.

			@ Reality means the all the information (include variables and the relationships) within the boundary of causal or informational influence between variables.

			@ This is the same as "if a tree falls in a forest" thought experiment.

			@

		% ----------------------------------------------------------------------------

@@

			%% our claim

@@

			\begin{figure}[H]
				\includegraphics[width=\textwidth]{WritingMaterials/SeperationOfCGandCortHierachy.pdf}
%				{Coarse-grain and sensory anatomical hierarchies}
			\end{figure}

@@

	\section{Conscious vs unconscious processing}
		\ideaBox{Now we can combine "Relation to empirical findings in neuroscience and studies of consciousness" and "About Phenomenology (conscious processing)" in to this}

	\section{Comparison with other theories}
		\ideaBox{Main points should be same/diff, our advantages, and predictions}

@@

@@

	\section*{=== backup ===}	
	\section*{Biological evidence of informational closure in neural system}
		\begin{ants}		
			% ============================================================================ %
			%                             sederberg2018learning                            %
			% ============================================================================ %

	\section*{Relation to empirical findings in neuroscience and studies of consciousness}

	\section*{About Phenomenology (conscious processing)}
\subsection{Perceptual overflow}
\subsection{Volition and freewill}
\begin{ants}
	@ Volition is a result of coarse-graining

	\section*{Theory predictions (Counter-intuitive prediction)}
